Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-03-11 ms.tex
fixed paragraph on cooling/conduction solutions

In addition to our standard set of solutions neglecting thermal
conduction and cooling, we explore a few test simulations including
these effects, as marked in Table \ref{table:models}. For solutions we
with large wind heating parameters ($\vwO \gsim 1200 km/s$ km/s), we
expect radiative cooling to have virtually no effect on the solution
for reasonable values of the mass return parameter.  For cusp galaxies
Thermally stable solutions are possible for values of the wind heating
parameter as low as $\vwO=300$ km/s. However, this will be dependent
on the value of the mass return parameter (and thus on the age of the
stellar population) and on the break radius, $\rb$. For $\vwO\simeq
300$ km/s, solutions with large $\rb$ will have large stagnation radii
and thus larger densities. Thus, solution with $v_w$=300 km/s
$\rb\gsim 100$ pc, would be thermally unstable.  The picture is
qualitatively similar for core galaxies. However, the stagnation
radius ``runs away'' to large radii at much smaller values of the wind
heating paramter ($\vwO\simeq 600 km/s$). Thus, thermal instability
sets in for higher values of $\vwO$ for core galaxies.

In practice we expect that the effective wind heating will
be or order $\sim 1000$ km/s if heating is dominated by young
stars as would be the case for small black holes. This region of
parameter space should be thermally stable. For higher mass
black holes heating would be dominated by the supernovae and black
hole feedback and would be comparable to the stellar velocity
dispersion of the galaxy. Since core galaxies dominate for large
$\Mbh$ we expect this region of parameter space to be thermally unstable.

From our analytic results (see equation~\eqref{eq:conduction}) and
direct numerical experiments, we expect that thermal conduction would
introduce at most order unity changes in our solutions. The conductive
heating flux saturates, so that at the stagnation radius the
conductive heating rate is comparable to the external heating rate.

>>>>

In addition to our standard set of solutions neglecting thermal conduction and cooling, we explore a few test simulations including these effects, as marked by dagger symbols in Table \ref{table:models}.  For solutions which are far from being thermally unstable when cooling is neglected (e.g. $M_{\bullet} = 10^{8}M_{\odot}$, $v_{w} = 600$ km s$^{-1}$, $r_{b} = 100$ pc, $\eta = 0.2$, $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}| = 76$), the effects of including radiative cooling on the key properties of the flow (stagnation radius, mass accretion rate, $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|$ ratio) are small.  However, for solutions in which cooling stability is marginal (e.g. $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}| \sim $few), including cooling decreases the value of $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|$ by a greater fraction.  Likewise, we find that the key properties of solutions including thermal conduction are always minor for our choice of the saturation parameter $\phi = 0.1$, and they act to offset the effects of radiative cooling, i.e. to make the flow more thermally stable (e.g.~\citealt{Zakamska&Narayan03}).
